Universal Anonymous Signatures

### 2022-08-05 prism-backend/research/gsac/formal-uas.tex
Updating proofs.

@@

\begin{definition}{(\UAS-acceptable functions)}
  \label{def:uas-acc-func}
  We say that a \fissue function chosen from some family \famfissue is
  \UAS-acceptable if its outputs are hiding with respect to its \upk and
  $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
  %
  Similarly, a \feval function chosen from some family \famfeval is
  \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
  respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
\end{definition}

@@

        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],\scid,\msg) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

@@

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=$\\
          \hspace*{5em}$\lbrace (\ccid_{0,i},\ccid_{1,i})
          \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\PUBUK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\   
          \cSig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\cscid_b,\msg,
          \feval) \\
          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforgeissue}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
        \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
        \gets \ExtractIssue(\trap,\utrans) \\
        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
        % \trans[\cid_i]) \\
        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
        \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) = \yissue:
        \pcreturn 1 \\
        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0
      }
      \vspace*{0.5em}

@@

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\cidu,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
  \attrs),\Issue(\isk,\cidi,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
attests attributes $\cattrs_i$. The user requests a signature on a commitment to
the user key, as well as on $\cid=(\cidi,\cidu)$ and the attributes in \attrs.
In addition, the user proves correct computation of the \fissue function set by
the issuer based on the $\cred_i$ credentials and its user public key.
This is essentially achieved through an execution of an \SBCM interactive
signing protocol with $\NIZKRel_{\Issue}$ as NP relation. Since \fissue is
evaluated by the user, but depends on the \cidi value chosen by the issuer, the
issuer first needs to send \cidi.
Then both interact to produce the \SBCM signature, where the
user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
\cattrs_i,\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the
issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
\rbrace_{i\in[n]})$. The credential \cred produced by the user is the result of
the interactive signing protocol, whereas the issuer produces $(\yissue,
\utrans)$, where \yissue is the output of \fissue, and \utrans is the
communication transcript of the signing protocol.% , which is a $(\Ccom,(\cid,\attrs),\lbrace
% \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple (see \appref{sapp:sbcm} for details).

@@

\begin{theorem}[Issuance anonymity of \CUASGen]
  \label{thm:issue-anonymity-uas}
  If the \SBCM scheme is blinding, the NIZK system used for $\NIZKRel_{\Issue}$ 
  is zero-knowledge, and \fissue is a \CUASGen-acceptable function, our \CUASGen
  construction satisfies issuance anonymity as defined in
  \defref{def:issue-anonymity-uas}.
\end{theorem}

>>>>

\jesus{Adding a \uid into \HU or \CU within an oracle that is executed by end
  users in the real world is a bit weird if not clarified. Some arguments may
  be possible.}

@@

\begin{definition}{(\UAS-acceptable \fissue functions)}
  \label{def:uas-acc-func}
  We say that a \fissue function chosen from some family \famfissue is
  \UAS-acceptable if, conditioned on it returning a non-zero value, the
  value it produces is indistinguishable from random.
  % %
  % Similarly, a \feval function chosen from some family \famfeval is
  % \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
  % respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
\end{definition}

@@

        \procedure{$\SIGN(\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \uid \gets \OWNR[\scid] \\
          \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],\scid,\msg) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

@@

        \procedure{$\CHALb(\oid,\cscid_{0,1}=
          \lbrace (\ccid_{0,i},\ccid_{1,i})
          \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcfor d\in\bin: \cuid_d \gets \OWNR[\cscid_d] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\PUBUK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\   
          \cSig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\cscid_b,\msg,
          \feval) \\
          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforgeissue}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
        \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
        \gets \ExtractIssue(\trap,\utrans) \\
        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
        % \trans[\cid_i]) \\
        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
        \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) \neq \yissue:
        \pcreturn 1 \\
        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
        \uid \in \HU \cup \CU: \pcreturn 1 \\
%        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0
      }
      \vspace*{0.5em}

@@

\todo{Need to make the $\cid_i$s explicity in the \SBCMVerify clauses of
  $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$.}
\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/nizk.tex}
  }
  \caption{CS specification of the NP relations used in \CUASGen.}
  \label{fig:nizkrels}
\end{figure}

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\cidu,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
  \attrs),\Issue(\isk,\cidi,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
attests attributes $\cattrs_i$. The user requests a signature on a commitment to
the user key, as well as on $\cid=(\cidi,\cidu)$ and the attributes in \attrs.
In addition, the user proves correct computation of the \fissue function set by
the issuer based on the $\cred_i$ credentials and its user public key.
This is essentially achieved through an execution of an \SBCM interactive
signing protocol with $\NIZKRel_{\Issue}$ as NP relation. Since \fissue is
evaluated by the user, but depends on the \cidi value chosen by the issuer, the
issuer first needs to send \cidi.
Then both interact to produce the \SBCM signature, where the
user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
\cattrs_i,\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the
issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
\rbrace_{i\in[n]})$. Observe that, within this protocol, the user sends a NIZK
proof $\NIZKproof_{\Issue}$ ensuring that it knows a valid witness $(\upk,\usk,
\lbrace (\cid_i,\cattrs_i,\cred_i)\rbrace_{i \in [n]},r)$ for the relation
$\NIZKRel_{\Issue}$. The credential \cred produced by the user is the result of
the interactive signing protocol, whereas the issuer produces $(\yissue,
\utrans)$, where \yissue is the output of \fissue, and \utrans is the
communication transcript of the signing protocol.% , which is a $(\Ccom,(\cid,\attrs),\lbrace
% \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple (see \appref{sapp:sbcm} for details).

@@

\begin{theorem}[Issuance anonymity of \CUASGen]
  \label{thm:issue-anonymity-uas}
  If the \SBCM scheme is blinding, the NIZK system used for $\NIZKRel_{\Issue}$ 
  is zero-knowledge, and \fissue is a \UAS-acceptable function, our \CUASGen
  construction satisfies issuance anonymity as defined in
  \defref{def:issue-anonymity-uas}.
\end{theorem}
